How to compute the fusion product of MV cycles in type A

### 2021-04-28 draft.tex
Fixed a typo.

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ scheme-theoretic fibre over a point $ s \in \AA$.

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
In this part we prove that the product 
% the ideal of 
% $Z'\ast_\AA Z''$ 
$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
% 
To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
%

>>>>

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
In this part we prove that the product 
% the ideal of 
% $Z'\ast_\AA Z''$ 
$b_{Z'}b_{Z''}\in\CC[N]$ can be computed from a ``minimal'' pair $(\tau',\tau'')$ of semistandard Young tableaux for the Lusztig data  $(n_\bullet(Z'),n_\bullet(Z''))$. 
% 
\rcom{I don't think we introduced $\CC[N]$ or the elements $b_Z$ yet. Should I talk about cluster algebras/exchange relations before this?}
To begin, let $\tau',\tau''$ be given and let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
%
